Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-22 paper/paper.tex

\subsection{More construction events after switching states}
Table \ref{tab:SW22_replication_50y} shows estimates for Equation \eqref{eq:sw22}. Figure \ref{fig:SW_replication} plots the coefficients to visualise how the effect evolves dynamically.

>>>>

\subsection{More construction events after switching states}

Table \ref{tab:SW22_replication_50y} shows estimates for Equation \eqref{eq:sw22}. Figure \ref{fig:SW_replication} plots the coefficients in column (1) to visualise how the effect evolves dynamically.

The
